Technique for \earlywarning\ detection of compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-17 method.tex
Asymptotic expression for LLOID
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1117 ccdd05d5-56c1-461a-bf98-85f6876523b4

>>>>

We can simplify this expression quite a bit by taking some limits that arise from sensible filter design.  In the limit of many templates, the cost of the decimation filters is negligible as compared to the cost of the interpolation filters.  Typically, we will design the interpolation filters with $N^\shortuparrow \lesssim \numsvdtmps$ so that the interpolation cost itself is negligible compared with the reconstruction cost.  Finally, if the number of basis templates per time slices $\numsvdtmps$ is not too small, the reconstruction cost dominates over the cost of accumulating the partial \SNR.  In these limits, the cost of \lloid\ is dominated by the basis filters themselves and the reconstruction, totaling $2 \sum_{s=0}^{S-1} f^s \numsvdtmps \left( \slicessamps + \numtmps \right)$ \flops.
